Synthesizing Quotient Lenses

### 2017-10-24 papers/QuotientLensSynth/main.tex
starting to restructure the intro

\begin{abstract}

{\em Lenses}~\cite{Lenses} specify bidirectional 
transformations between different data formats.  Writing a single lens
rather than two separate uni-directional transformations saves both
keystrokes and bugs, by reducing redundancy and by automatically
guaranteeing strong ``lens laws'' ensuring that the forward and backward
transformations interact well.  
%
{\em Quotient lenses}~\cite{quotientlenses} are a generalization of lenses
where each of the data formats is quotiented by some equivalence relation
and the lens laws are taken modulo equivalence.  This allows lenses to be
both simpler and more flexible, since whole equivalence classes of data
values can be handled all at once and inessential details like whitespace
and ordering of fields can be ignored.

\smallskip

@@

\smallskip

In this paper, we address both of these issues.  First, we propose a novel
language of {\em Quotient Regular Expressions}, or QREs, which allows
programmers to specify a broad class of equivalence relations over regular
languages using a compact and convenient notation in which the regular
language and its equivalence classes are captured by a single expression.
We then define {\em QRE lenses}, a class of bijective quotient lenses that
are typed using QREs, and we show how to {\em synthesize} QRE lenses from their
QRE types and a set of input-output examples.  We demonstrate the
practicality of this approach by synthesizing QRE lenses between several
real-world data formats from the {\tt data.gov} database.
\end{abstract}

\section{Introduction}
A {\em lens} $\ell$ is a {\em bidirectional transformation} between a source
type $S$ and a target type $T$ in which the forward transformation
$\ell.\get$ and the backward transformation $\ell.\lput$ satisfy certain
round-tripping laws such as invertibility.

>>>>

\begin{abstract} 
{\em Lenses}~\cite{Lenses} specify bidirectional 
transformations between different data formats.
\saz{The old abstract read more like an introduction, so we modified it to be
  the ``new'' introduction.}
\end{abstract}

\section{Introduction}
A {\em lens} $\ell$ is a {\em bidirectional transformation} between a source
type $S$ and a target type $T$ in which the forward transformation
$\ell.\get$ and the backward transformation $\ell.\lput$ satisfy certain
round-tripping laws such as invertibility.
 Writing a single lens
rather than two separate uni-directional transformations saves both
keystrokes and bugs, by reducing redundancy and by automatically
guaranteeing strong ``lens laws'' ensuring that the forward and backward
transformations interact well.

{\em Quotient lenses}~\cite{quotientlenses} are a generalization of lenses
where each of the data formats is quotiented by some equivalence relation
and the lens laws are taken modulo equivalence.  This allows lenses to be
both simpler and more flexible, since whole equivalence classes of data
values can be handled all at once and inessential details like whitespace
and ordering of fields can be ignored.

@@

This paper addresses both of these issues.  First, in Section~\ref{example} we
explain the difficulties of programming with quotient lenses and show, by way of
example, how our novel language of {\em Quotient Regular Expressions}, or QREs
addresses those difficulties.  Quotient regular expressions allow programmers to
specify a broad class of equivalence relations over regular languages using a
compact and convenient notation in which the regular language and its
equivalence classes are captured by a single expression.  We then define {\em
  QRE lenses}, a class of bijective quotient lenses that are typed using QREs,
and we show how to {\em synthesize} QRE lenses from their QRE types and a set of
input-output examples.  We demonstrate the practicality of this approach by
synthesizing QRE lenses between several real-world data formats from the {\tt
  data.gov} database.

\saz{There is still some redundancy between the following contributions list and
  the paragraph above.}

\section{Lenses and Quotient Regular Expressions by Example}
